The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2019-06-19 razzo-methods.tex
Add figs

>>>>

\subsection{Quantifying the impact of the speciation model}
\richel{this is a proposal}

To quantify the impact of the speciation model, we propose to
use impact = complete error - baseline error / complete error.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{razzo-figures/pir_ex_3_errors.png}
  \caption{
    Uses Yule tree, impact of speciation model should be low
  }
  \label{fig:results}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{razzo-figures/pir_ex_6_errors.png}
  \caption{
    Uses non-standard tree, impact of speciation model should be high
  }
  \label{fig:results}
\end{figure}
